### 2013-10-01 Rcode/test.ash.Rmd
updated ash to use normalmix methods rather in mix.R to compute posterior mean, PositiveProb, NegativeProb etc

@@

#Test VBEM
abf = rbind(c(1,0,0,0),c(0,1,0,0),c(0,0,1,0),c(0,0,1,0),c(0,0,1,0))
eps = 1e-10
abf[abf==0] = eps #replace 0 with small number
print(all.equal(VBEM(abf,c(1,1,1,1))$post,c(2,2,4,1)))
print(all.equal(VBEM(abf,c(1,2,1,1))$post,c(2,3,4,1)))

@@

ss = simdata(10000,8000,0,2,1)

system.time((beta.ash=ash(ss$betahat,ss$betasd)))
system.time((beta.ash.auto = ash(ss$betahat, ss$betasd,auto=TRUE)))
system.time((beta.ash.vb.uniform = ash(ss$betahat, ss$betasd,auto=TRUE, VB=TRUE, prior="uniform")))
system.time((beta.ash.vb.null = ash(ss$betahat, ss$betasd,auto=TRUE, VB=TRUE, prior=NULL)))

@@

hist(ss$beta,prob=TRUE,breaks=seq(-7,7,length=20))
x= seq(-4,4,length=10000)
lines(x,density(beta.ash,x),col=2)
lines(x,density(beta.ash.auto,x),col=3)
lines(x,density(beta.ash.vb.uniform,x),col=4)
lines(x,density(beta.ash.vb.null,x),col=5)
beta.ash$fitted.f
beta.ash.auto$fitted.f
beta.ash.vb.uniform$fitted.f
beta.ash.vb.null$fitted.f

beta.ash.vb.uniform$fit$loglik
beta.ash.vb.uniform$fit$converged

>>>>

```{r}
source("ash.R")
set.seed(100)
#Test VBEM
abf = rbind(c(1,0,0,0),c(0,1,0,0),c(0,0,1,0),c(0,0,1,0),c(0,0,1,0))
eps = 1e-10
abf[abf==0] = eps #replace 0 with small number
print(all.equal(VBEM(abf,c(1,1,1,1))$post,c(2,2,4,1)))
print(all.equal(VBEM(abf,c(1,2,1,1))$post,c(2,3,4,1)))

@@

@@

```{r}
ss = simdata(10000,8000,0,2,1)
beta.ash=ash(ss$betahat,ss$betasd)

system.time((post = posterior_dist(beta.ash$fitted.g,ss$betahat,rep(ss$betasd,length(ss$betahat)))))
system.time((PositiveProb = pnormmix(0,post$pi,post$mu,post$sigma,lower.tail=FALSE)))

system.time((PP2 = 1-cdf_post(beta.ash$fitted.g, 0, ss$betahat,rep(ss$betasd,length(ss$betahat)))))    
all.equal(PP2,PositiveProb)
```

```{r}
system.time((beta.ash=ash(ss$betahat,ss$betasd)))
system.time((beta.ash.auto = ash(ss$betahat, ss$betasd,auto=TRUE)))
system.time((beta.ash.vb.uniform = ash(ss$betahat, ss$betasd,auto=TRUE, VB=TRUE, prior="uniform")))
system.time((beta.ash.vb.null = ash(ss$betahat, ss$betasd,auto=TRUE, VB=TRUE, prior=NULL)))

@@

hist(ss$beta,prob=TRUE,breaks=seq(-7,7,length=20))
x= seq(-4,4,length=10000)
lines(x,density(beta.ash,x),col=2)
lines(x,density(beta.ash.auto,x),col=3)
lines(x,density(beta.ash.vb.uniform,x),col=4)
lines(x,density(beta.ash.vb.null,x),col=5)
summary(beta.ash)
summary(beta.ash.auto)
summary(beta.ash.vb.uniform)
summary(beta.ash.vb.null)
```
